Selective electroporation of the viral envelope

### 2021-03-29 documents/pure_electroporation.tex
Electroporation
Transmembrane
Triangle wave works

%!TeX root = pure_electroporation
\documentclass[fleqn,10pt]{article}

\include{preamble}
\begin{document}

\title{Selective electroporation of the viral envelope}
\author{\small{Daniel Correia\orcidlink{0000-0002-9353-0216} (therobotist@gmail.com), Ontario, Canada.}}
\date{March 21 2021}

\flushbottom 
\maketitle
\thispagestyle{empty}

@@

@@

@@

Critically, Gimsa and Schnelle data, both on influenza, seems to suggest a core conductivity of 0.1 to 1 milliSiemens/m (1000 to 10000 $\Omega \cdot m$). This is far less conductive than cytoplasm or nucleoplasm, each on the order of 1 S/m (1 $\Omega \cdot m$) \cite{Study2001}.

@@

>>>>

%!TeX root = pure_electroporation
\documentclass[fleqn,10pt]{paper}

\usepackage[left=2cm,right=2cm,
top=0.5cm,
bottom=1.5cm,%
headheight=11pt,%
letterpaper]{geometry}

\include{preamble}

\begin{document}

\title{Selective electroporation of the viral envelope}
\author{\footnotesize{Daniel Correia\orcidlink{0000-0002-9353-0216} \footnote{therobotist@gmail.com, Ontario, Canada.}}}
\date{\small{March 21 2021}}

\flushbottom 
%%\maketitle
%\begingroup
%\let\center\flushleft
%\let\endcenter\endflushleft
\maketitle
%\endgroup

\thispagestyle{empty}

@@

Electroinsertion of proteins into membranes\cite{Clinical1996}; to provoke a local immune response near affected tissues,

@@

The trapping experiments we use were conducted at

@@

Critically, Gimsa and Schnelle data, both on influenza, seems to suggest a core conductivity of 0.8 to 0.1 milliSiemens/m (1000 to 10000 $\Omega \cdot m$), using a medium conductivity of 74 mS/m and 3 mS/m, respectively. This is far less conductive than cytoplasm or nucleoplasm, each on the order of 1 S/m (1 $\Omega \cdot m$) \cite{Study2001}.

% if this is correct, scaling linearly:
% like 60 % water in core  * (1 S/m / 0.074) would get us to 1 mS/m.

% absolute pessimistic, using 0.8 mS/m and Schnelle's medium conductivity, would get us 0.008 * 0.6 * (1/0.003) = 1.6 S/m

@@

Kotnik-simulchouski

(Helmholz)
